\begin{frame}[allowframebreaks]{Bibliographie}
  \begin{thebibliography}{10}
    \bibitem[Billinghurst \textit{et al.} 2005]{Billinghurst2005}
      Mark Billinghurst, Raphael Grasset, Julian Looser.
      \newblock Designing augmented reality interfaces.
      \newblock ACM SIGGRAPH Computer Graphics, 39(1), 17-22.

    \bibitem[Ens \textit{et al.} 2014]{Ens2014}
      Barrett M. Ens, Rory Finnegan, Pourang P. Irani.
      \newblock The personal cockpit: A spatial interface for effective task switching on head-worn displays.
      \newblock CHI 2014.

    \bibitem[Grubert \textit{et al.} 2015]{Grubert2015}
      Jens Grubert, Matthias Heinisch, Aaron J. Quigley, Dieter Schmalstieg.
      \newblock MultiFi: Multi fidelity interaction with displays on and around the body.
      \newblock CHI 2015.

    \bibitem[Heun \textit{et al.} 2016]{Heun2016}
      Valentin Heun, James Hobin, Pattie Maes.
      \newblock Reality Editor: Programming Smarter Objects.
      \newblock UbiComp 2013.

    \bibitem[Lee \textit{et al.} 2013]{Lee2013}
      Jinh Lee, Alex Olwal, Hiroshi Ishii, Cati Boulanger.
      \newblock SpaceTop: Integrating 2D and spatial 3D interactions in a see-through desktop environment.
      \newblock CHI 2013.

    \bibitem[Liu \textit{et al.} 2014]{Liu2014}
      Can Liu, Olivier Chapuis, Michel Beaudouin-Lafon, Eric Lecolinet, Wendy E. Mackay.
      \newblock Effects of display size and navigation type on a classification task.
      \newblock CHI 2014.

    \bibitem[Piumsomboon \textit{et al.} 2013]{Piumsomboon2013}
      Thammathip Piumsomboon, Adrian Clark, Mark Billinghurst, Andy Cockburn.
      \newblock User-defined gestures for augmented reality.
      \newblock CHI 2013.

    \bibitem[Pfeuffer \textit{et al.} 2017]{Pfeuffer2017}
      Ken Pfeuffer, Benedikt Mayer, Diako Mardanbegi, Hans Gellersen.
      \newblock Gaze + pinch interaction in virtual reality.
      \newblock UIST 2017.

    \bibitem[Serrano \textit{et al.} 2015]{Serrano2015}
      Marcos Serrano, Barrett Ens, Xing-Dong Yang, Pourang Irani.
      \newblock Gluey: Developing a head-worn display interface to unify the interaction experience in distributed display environments.
      \newblock MobileHCI 2015.

    \bibitem[Serrano \textit{et al.} 2015a]{Serrano2015a}
      Marcos Serrano, Barrett Ens, Xing-Dong Yang, Pourang Irani.
      \newblock Desktop-Gluey: Augmenting desktop environments with wearable devices.
      \newblock MobileHCI 2015.

    \bibitem[Steptoe2013]{Steptoe2013}
      William Steptoe.
      \newblock AR-Rift (Part 1).
      \newblock \url{http://willsteptoe.com/post/66968953089/ar-rift-part-1}.

    \bibitem[Taylor \textit{et al.} 2016]{Taylor2016}
      Jonathan Taylor, Lucas Bordeaux, Thomas J. Cashman, Bob Corish, Cem Keskin, Toby Sharp, Eduardo Soto, David Sweeney, Julien P. C. Valentin, Benjamin Luff, Arran Topalian, Erroll Wood, Sameh Khamis, Pushmeet Kohli, Shahram Izadi, Richard Banks, Andrew W. Fitzgibbon, Jamie Shotton.
      \newblock Efficient and precise interactive hand tracking through joint, continuous optimization of pose and correspondences.
      \newblock ACM Transactions on Graphics, 35(4), 1-12.

    \bibitem[Wobbrock \textit{et al.} 2009]{Wobbrock2009}
      Jacob O. Wobbrock and Meredith Ringel Morris and Andrew D. Wilson.
      \newblock User-defined gestures for surface computing.
      \newblock CHI 2009.
  \end{thebibliography}
\end{frame}