\begin{frame}[allowframebreaks]{Bibliographie}
  \begin{thebibliography}{10}
    \bibitem[Baudisch2002]{Baudisch2002}
      Patrick Baudisch, Nathaniel Good, Victoria Bellotti, Pamela K. Schraedley.
      \newblock Keeping things in context: A comparative evaluation of focus plus context screens, overviews, and zooming.
      \newblock CHI 2002.

    \bibitem[Billinghurst2005]{Billinghurst2005}
      Mark Billinghurst, Raphael Grasset, Julian Looser.
      \newblock Designing augmented reality interfaces.
      \newblock ACM SIGGRAPH Computer Graphics, 39(1), 17-22.

    \bibitem[Ens2014]{Ens2014}
      Barrett M. Ens, Rory Finnegan, Pourang P. Irani.
      \newblock The personal cockpit: A spatial interface for effective task switching on head-worn displays.
      \newblock CHI 2014.

    \bibitem[Heun2016]{Heun2016}
      Valentin Heun, James Hobin, Pattie Maes.
      \newblock Reality Editor: Programming Smarter Objects.
      \newblock UbiComp 2013.

    \bibitem[Lee2013]{Lee2013}
      Jinh Lee, Alex Olwal, Hiroshi Ishii, Cati Boulanger.
      \newblock SpaceTop: Integrating 2D and spatial 3D interactions in a see-through desktop environment.
      \newblock CHI 2013.

    \bibitem[Pfeuffer2017]{Pfeuffer2017}
      Ken Pfeuffer, Benedikt Mayer, Diako Mardanbegi, Hans Gellersen.
      \newblock Gaze + pinch interaction in virtual reality.
      \newblock UIST 2017.

    \bibitem[Serrano2015]{Serrano2015}
      Marcos Serrano, Barrett Ens, Xing-Dong Yang, Pourang Irani.
      \newblock Gluey: Developing a head-worn display interface to unify the interaction experience in distributed display environments.
      \newblock MobileHCI 2015.

    \bibitem[Taylor2016]{Taylor2016}
      Jonathan Taylor, Lucas Bordeaux, Thomas J. Cashman, Bob Corish, Cem Keskin, Toby Sharp, Eduardo Soto, David Sweeney, Julien P. C. Valentin, Benjamin Luff, Arran Topalian, Erroll Wood, Sameh Khamis, Pushmeet Kohli, Shahram Izadi, Richard Banks, Andrew W. Fitzgibbon, Jamie Shotton.
      \newblock Efficient and precise interactive hand tracking through joint, continuous optimization of pose and correspondences.
      \newblock ACM Transactions on Graphics, 35(4), 1-12.
  \end{thebibliography}
\end{frame}