\begin{frame}[allowframebreaks]{References}
  \begin{thebibliography}{10}
    \bibitem[Ens \textit{et al.} 2014]{Ens2014}
      Barrett M. Ens, Rory Finnegan, Pourang P. Irani.
      \newblock The personal cockpit: A spatial interface for effective task switching on head-worn displays.
      \newblock CHI 2014.

    \bibitem[Grubert \textit{et al.} 2015]{Grubert2015}
      Jens Grubert, Matthias Heinisch, Aaron J. Quigley, Dieter Schmalstieg.
      \newblock MultiFi: Multi fidelity interaction with displays on and around the body.
      \newblock CHI 2015.

    \bibitem[Liu \textit{et al.} 2014]{Liu2014}
      Can Liu, Olivier Chapuis, Michel Beaudouin-Lafon, Eric Lecolinet, Wendy E. Mackay.
      \newblock Effects of display size and navigation type on a classification task.
      \newblock CHI 2014.

    \bibitem[Piumsomboon \textit{et al.} 2013]{Piumsomboon2013}
      Thammathip Piumsomboon, Adrian Clark, Mark Billinghurst, Andy Cockburn.
      \newblock User-defined gestures for augmented reality.
      \newblock CHI 2013.

    \bibitem[Serrano \textit{et al.} 2015]{Serrano2015}
      Marcos Serrano, Barrett Ens, Xing-Dong Yang, Pourang Irani.
      \newblock Desktop-Gluey: Augmenting desktop environments with wearable devices.
      \newblock MobileHCI 2015.

    \bibitem[Steptoe2013]{Steptoe2013}
      William Steptoe.
      \newblock AR-Rift (Part 1).
      \newblock \url{http://willsteptoe.com/post/66968953089/ar-rift-part-1}.

    \bibitem[Wobbrock \textit{et al.} 2009]{Wobbrock2009}
      Jacob O. Wobbrock and Meredith Ringel Morris and Andrew D. Wilson.
      \newblock User-defined gestures for surface computing.
      \newblock CHI 2009.
  \end{thebibliography}
\end{frame}